---
title: "proje_rak"
author: "Rafet Ali Kaba"
date: "2023-02-24"
output:
  pdf_document: default
  html_document:
    df_print: paged
---
## PROJECT

In this project, we will analysis whether the game makers earned more than the games they released for ps4 or ps3.

## MY CODES

I insatalled my libraries first

```{r}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(tidyr)
library(readr)
library(stringr)
```

I import my dataset and examine it and make it more organized and editable

```{r}
oyunlar<-read.csv("game.csv")
oyunlar$total_sales<-gsub("N/A","",oyunlar$total_sales)
oyunlar$total_sales<-str_replace(oyunlar$total_sales,"m","")
oyunlar$total_sales<-str_replace(oyunlar$total_sales,".","")
oyunlar$total_sales<-as.numeric(oyunlar$total_sales,na.rm=TRUE)
toplam_total_sales<-sum(oyunlar$total_sales,na.rm=TRUE)
```

Then i separate the platform

```{r}
ps4<- oyunlar%>%
  filter(platform=="PS4")

ps3<- oyunlar%>%
  filter(platform=="PS3")
```

Then I find the total earnings of the publishers from the platform and turn them into a data frame.

```{r}
eagames<-oyunlar%>%
  filter(publisher=="Electronic Arts")%>%
  filter(platform=="PS4")%>%
  summarise(toplamsatis=sum(total_sales,na.rm=TRUE))

rockstar<- oyunlar%>%
  filter(publisher=="Rockstar Games")%>%
  filter(platform=="PS4")%>%
  summarise(toplamsatis=sum(total_sales,na.rm=TRUE))

activision<- oyunlar%>%
  filter(publisher=="Activision")%>%
  filter(platform=="PS4")%>%
  summarise(toplamsatis=sum(total_sales,na.rm=TRUE))

sony<- oyunlar%>%
  filter(publisher=="Sony Interactive Entertainment")%>%
  filter(platform=="PS4")%>%
  summarise(toplamsatis=sum(total_sales,na.rm=TRUE))

ubisoft<- oyunlar%>%
  filter(publisher=="Ubisoft")%>%
  filter(platform=="PS4")%>%
  summarise(toplamsatis=sum(total_sales,na.rm=TRUE))


eagames2<-oyunlar%>%
  filter(publisher=="Electronic Arts")%>%
  filter(platform=="PS3")%>%
  summarise(toplamsatis=sum(total_sales,na.rm=TRUE))

rockstar2<- oyunlar%>%
  filter(publisher=="Rockstar Games")%>%
  filter(platform=="PS3")%>%
  summarise(toplamsatis=sum(total_sales,na.rm=TRUE))

activision2<- oyunlar%>%
  filter(publisher=="Activision")%>%
  filter(platform=="PS3")%>%
  summarise(toplamsatis=sum(total_sales,na.rm=TRUE))

sony2<- oyunlar%>%
  filter(publisher=="Sony Interactive Entertainment")%>%
  filter(platform=="PS3")%>%
  summarise(toplamsatis=sum(total_sales,na.rm=TRUE))

ubisoft2<- oyunlar%>%
  filter(publisher=="Ubisoft")%>%
  filter(platform=="PS3")%>%
  summarise(toplamsatis=sum(total_sales,na.rm=TRUE))

toplam2<-data.frame(eagames2,rockstar2,activision2,sony2,ubisoft2)
rownames(toplam2)<-"PS3"
colnames(toplam2)<-c("EA","Rock Star","Activision","Sony","Ubisoft")
```

```{r}
toplamsatislar<-data.frame(eagames,rockstar,activision,sony,ubisoft)
rownames(toplamsatislar)<-"PS4"
colnames(toplamsatislar)<-c("EA","Rock Star","Activision","Sony","Ubisoft")

toplam2<-data.frame(eagames2,rockstar2,activision2,sony2,ubisoft2)
rownames(toplam2)<-"PS3"
colnames(toplam2)<-c("EA","Rock Star","Activision","Sony","Ubisoft")

toplamsatislar<-rbind(toplamsatislar,toplam2)

toplam1<-t(toplamsatislar)
toplam1<-data.frame(toplam1)

```

and finally I visualize this total sales data.

```{r}
graph1<-ggplot(toplam1, aes(x=toplam1[,1],y=row.names(toplam1)))
  
graph1<-graph1+labs(x="Total Sales",y="Game Companies",title="PS 4")+geom_point(color="blue",size=7,shape=16)

graph2<-ggplot(toplam1, aes(x=toplam1[,2],y=row.names(toplam1)))
  
graph2<-graph2+labs(x="Total Sales",y="Game Companies",title="PS 3")+geom_point(color="green",size=7,shape=16)
```

```{r}
graph1
```

```{r}
graph2
```





